---
title: "Repoducible Pitch"
author: "Adam Carr"
date: "18/03/2017"
output: 
   slidy_presentation:
      theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk("ui.R")
knitr::read_chunk("server.R")
```

## What is the application

- It is a simple app that predicts the weight of a chick based on the the diet selected and time in days the chick was on the diet.
- It is based on easy to obtain information - The ChickWeight dataset available in the datasets package within R.
- It is basically a submission for the coursea course - data products.

## The prediction model (includes R code)

- a simple linear model is created based on the ChickWeight data for the given diet.

```{r}
data("ChickWeight")
input.diet <- "1"; input.days <- 9 # these would be an input to the app!
# simple model
mdl <- lm(weight ~ Time,data=ChickWeight[ChickWeight$Diet==input.diet,])
```

## How the model is used 1 
- a plot is generated:
```{r plot, eval=TRUE, fig.height=3, fig.width=5, fig.align='center'}
plot(predict(mdl, data.frame(Time=c(1:22))),
     type="b",col="blue",
     main=sprintf("Predicted weight for chick on experimental diet %s",input.diet),
     xlab="time on diet (days)", ylab="Weight (gm)")
abline(v=input.days,col="red")
abline(h=predict(mdl, data.frame(Time=c(input.days))),col="red")
```

## How the model is used 2


- a prediction is made
```{r}
pred.wt <- sprintf("[%s gm]", predict(mdl, data.frame(Time=c(input.days))))
```

- The result : `r pred.wt`



